RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-06 rmd/reply1.Rmd
Update reply1.Rmd

@@

@@

I was expecting that high productivity you might also see some occupancy changes but maybe for different reasons than low productivity. I wondered if at high productivity you could get increased trophic control where P controls C because it gets biomass from C and B. Also, as P grows it reduces the amount of B consumed by C (which should be increasingly dynamically unstable)? Here I was wondering if the more structural change without occupancy at high productivity might be a parameter limitation based on the levels of r that were used, also the way that you use r as a surrogate of productivity. Often carrying capacity is implicated as a factor in productivity as it sets the level for the amount of material that moves around in the modelled system. I raise these questions because I am used to thinking about the dynamical implications of food webs in terms of the parameters but also the populations as these both determine the strength of interactions (in terms of flux of material in linkages between species). And K can limit the potential for population sizes and has known implications on stability etc..

>>>>

> Thank you, please see our response below.

@@

> We have revisited our model in light of comments from Reviewer 1. In the revised version, the parameter $a_{BP}$ changes how quickly the intraguild predator shifts its prey from intraguild prey to basal species as B increases. We have clarified this point and explanations for the "structural constraint" (we have avoided to use this vague term throughout the ms).

@@

> In light of comments from Reviewer 1, we have reanalyzed and fully re-structured Results and Discussion according to the new results. The above statement does not hold in the revised MS, so they have been removed.

I was expecting that high productivity you might also see some occupancy changes but maybe for different reasons than low productivity. I wondered if at high productivity you could get increased trophic control where P controls C because it gets biomass from C and B. Also, as P grows it reduces the amount of B consumed by C (which should be increasingly dynamically unstable)?

Here I was wondering if the more structural change without occupancy at high productivity might be a parameter limitation based on the levels of r that were used, also the way that you use r as a surrogate of productivity. Often carrying capacity is implicated as a factor in productivity as it sets the level for the amount of material that moves around in the modelled system. I raise these questions because I am used to thinking about the dynamical implications of food webs in terms of the parameters but also the populations as these both determine the strength of interactions (in terms of flux of material in linkages between species). And K can limit the potential for population sizes and has known implications on stability etc..
